TacticToe: Learning the Game of Tactics

### 2018-02-08 tactictoe_jv.tex
problem: wip

\paragraph{Two ways of representing a formulas.}\todo{RK: Actually I don't know what two ways you mean...?}

@@

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function that takes a goal (or proof obligation) and returns a list of goals together with a validation function.
\todo{flesh the below out}
Input of the prediction: goal If a tactic produces no goals then its input goal is solved.
Define tactical etc maybe import graphic that explain how tactic works form the
presentations.
mention proof obligations (use this word) return by a tactic.

@@

\section{Proof Search Tree}\label{sec:prelim}

@@

We can also judge the productivity of a tactic by its contribution to the
search
tree.

\begin{definition} (Productive tactic)
The application of a tactic on an open goal is called productive if and only if
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we
interrupt tactics after a short amount of time (0.05 seconds).
\item It does not loop. Its output does not contain any goals that appears in
its ancestor nodes.
\item It is not a parallel step. Its output is not equal or a superset
of a list of goals produced from the same open goal.
\end{itemize}

@@

\begin{definition}\label{def:desc}(Children, descendant, active node)\\
We now define what are the children and the descendants of a node $a$. The
children of a relative to a goal $g$ in $G(a)$
is the set of nodes produced by tactics applied to $g$:
\[\mathit{Children}(g) = \lbrace A(g,t)\in \mathbb{A}\ |\ t \in T(g) \rbrace\]

We define the children of a node $a$ by:
\[\mathit{Children}(a) = \bigcup_{g \in G(a)} \mathit{Children}(g) \]

And the descendants of $a$ by:
\begin{align*}
\mathit{Descendant}^{0}(a) &=_{def} \lbrace a \rbrace \\
\mathit{Descendant}^{n+1}(a) &=_{def} \bigcup_{a' \in \mathit{Descendant}^{n}(a)}
\mathit{Children}(a') \\
\mathit{Descendant}(a) &=_{def} \bigcup_{n \in \mathbb{N}} \mathit{Descendant}^n(a)\\
\end{align*}

@@

\subsection{Feature Extraction}\label{sec:features}
The three objects considered are different representation of mathematical
formulas. Therefore, we start by describing which features we extract can
extract terms. From there, we extend the extraction mechanism
to goals, theorems and lists of goals. Duplicated features are always removed
so that each object has an associated set of features.

@@

In order to speed up the predictions during the search for a proof of a
conjecture $c$, we preselect 500 tactic-goal pairs and theorems.
Preselection for list of goals is induced by the preselection of input
goals in tactic-goal pairs. Those will be the only objects available to
\tactictoe's search algorithm for proving $c$.

>>>>

\paragraph{Goals and theorems.} 
A goal is represented as a sequent. Each sequent is composed of 
a list of assumptions and a conclusion which are higher-order logic formulas. 
When a goal is proven, it becomes a theorem. And if the developer gives it a 
name then we refer to it as a top-level theorem.

@@

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function 
that takes a goal (or proof obligation) and returns a list of goals together 
with a validation function. \todoi{do not mention validation?}

@@

\section{Preliminaries}\label{sec:prelim}

@@

\begin{definition}\label{def:desc}(Children, descendant, active node)\\
The children of a goal $g$ is a set of nodes defined by:
\[\mathit{Children}(g) = \lbrace A(g,t)\in \mathbb{A}\ |\ t \in T(g) \rbrace\]

By extension, we define the children of a node $a$ by:
\[\mathit{Children}(a) = \bigcup_{g \in G(a)} \mathit{Children}(g) \]

The descendants of $a$ by:
\begin{align*}
\mathit{Descendant}^{0}(a) &=_{def} \lbrace a \rbrace \\
\mathit{Descendant}^{n+1}(a) &=_{def} \bigcup_{a' \in \mathit{Descendant}^{n}(a)}
\mathit{Children}(a') \\
\mathit{Descendant}(a) &=_{def} \bigcup_{n \in \mathbb{N}} \mathit{Descendant}^n(a)\\
\end{align*}

And the ancestors of $a$ by:
\[\mathit{Ancestors}(a) =_{def} \lbrace b \in \mathbb{A} \ | \ a \in 
Descendant(b) \rbrace\]

We can now judge the productivity of a tactic by its contribution to the
search tree.

\begin{definition} (Productive tactic)
The application of a tactic on an open goal is called productive if and only if
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we
interrupt tactics after a short amount of time (0.05 seconds).
\item It does not loop. Its output does not contain any goals that appears in
the ancestor of the node of the current 
goal.
\item It is not a parallel step. Its output is not equal or a superset
of a list of goals produced from the same open goal.
\end{itemize}

@@

@@

\subsection{Feature Extraction}\label{sec:features}
The three objects considered are different representation of mathematical
formulas. Therefore, we start by describing features for terms. From there, we 
extend the extraction mechanism
to goals, theorems and lists of goals. Duplicated features are always removed
so that each object has an associated set of features.

@@

In order to speed up the predictions during the search for a proof of a
conjecture $c$, we preselect 500 tactic-goal pairs and 500 theorems and a 
larger number of list of goals induced by the selection of tactic-goal pairs. 
Preselected objects will 
be the only objects available to \tactictoe's search algorithm for proving $c$.
